---
title: "10-import"
output: html_document
---

I will look at 2018 mass shooting data that we used in previous class. I would like to see what states seem to have the biggest problems with this. I would also like to look at the deadliness/injurty rate of shootings relative to otheres within the state.

Hopefully this can help me identify states where this is large problem and where this isnt. Additionally I want to see what are the deadliest/injury fullest (?) shootings.

# librarys
```{r}
library(tidyverse)
library(janitor)
library(assertr)
library(dplyr)
library(ggplot2)
```

# import data set
```{r}
# import shooting data
s_data <- read_csv("shooting_data.csv", 
    # update column types appropriatly
    # killed and wounded are integers not doubles - have to be whole numbers
    col_types = cols(killed = col_integer(), 
        wounded = col_integer())) %>% 
  # clean names to remove spaces and special casings
  clean_names()

# use assertr statements to check killed and wounded are reasonable
s_data <- s_data %>% 
  # killed needs to be non negative
  assert(within_bounds(0,Inf), killed) %>% 
  # wounded needs to be non negative
  assert(within_bounds(0,Inf), wounded)
```

