---
title: "assign4"
output: html_notebook
---

```{r}
library(lubridate)
library(tidyverse)
library(RVerbalExpressions)
```


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 

```{r}
floor_date(unit = "year", today()) +
  months(0:11)
```

Write a function that given your birthday (as a date), returns how old you are in years.

```{r}
birthday_func <- function(birthday) {
  year(now()) - year(ymd(birthday))
}

birthday_func(ymd(19960827))
```

Write a function that given your birthday, returns the day of the week you were born on. 

```{r}
birth_day <- function(birthday){
  wday(ymd(birthday), label = T)
}
birth_day(ymd(19960827))
```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)

```{r}
str_view(stringr::words, ".......", match = TRUE)

seven_letters.rx <- rx() %>%
  rx_start_of_line() %>% 
  rx_alpha() %>% 
  rx_multiple(min = 7) %>% 
  rx_end_of_line()
str_view(stringr::words, seven_letters.rx, match = TRUE)
```


## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)

```{r}
str_subset(stringr::words, "^[^aeiou]+$")

vowel_check.rx <- rx() %>% 
  rx_start_of_line() %>% 
  rx_anything_but('aeiou') %>% 
  rx_end_of_line()
words[str_detect(stringr::words, vowel_check.rx)]
```

Empirically verify the rule “i before e except after c”.

```{r}
# case where wrong
str_subset(stringr::words, "(cei)")

words[str_detect(stringr::words, "cei")]
```

Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.

```{r}
possible_nums <- c("636-346-2805", "636/346/2805", "636.346.2805", "636 346 2805","(636) 346 2805", "(636)-346-2805")
# didnt split just used or (|)
phone <- rx() %>%
  rx_start_of_line() %>%
  rx_maybe("(") %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>%
  rx_maybe(")") %>%
  rx_any_of("/ .-") %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>%
  rx_any_of("/ .-") %>%
  rx_digit() %>%
  rx_repeat_previous(4) %>%
  rx_end_of_line() 
phone

str_view(possible_nums, phone, match = T)
```

# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

 ---- check 10-import

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

 ---- check 20-feature-engineering

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

